Open archaeology, open source?

### 2023-10-17 analysis/_04-open_archaeology.qmd
Update license data
Adding Zack's manual coding of repos GitHub couldn't automatically recognise; and simplifying the table by abbreviating license names and merging different versions of the same license

@@

```{r tbl-repo-licenses}
#| tbl-cap: Summary of licenses used by projects with GitHub repositories.
oarch |>
  hoist(gh_repo_info, license = list("license", 1, "name")) |>
  count(license) |>
  mutate(license = replace_na(license, "None detected")) |>
  arrange(-n) |>
  gt() |>
    cols_label(license = "License", n = "N")
```

>>>>

```{r data-licenses}
oarch_licenses <- read_csv(here("analysis/data/raw_data/open-archaeo_licenses.csv"))
oarch_licenses |>
  select(gh_repo = url, other_license = license) |>
  right_join(oarch, by = "gh_repo") |>
  hoist(gh_repo_info, license = list("license", 1, "spdx_id")) |>
  mutate(license = if_else(license == "NOASSERTION", other_license, license)) |>
  select(-other_license) ->
  oarch
```

```{r tbl-repo-licenses}
#| tbl-cap: Summary of licenses used by projects with GitHub repositories
# TODO: group small categories into "other"
oarch |>
  mutate(license = str_remove(license, "-?\\d\\.\\d$")) |>
  count(license) |>
  mutate(license = replace_na(license, "None detected")) |>
  arrange(-n) |>
  gt() |>
    cols_label(license = "License", n = "N")
```

@@
